%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
 \cventry
     {Lei Zhou, Fengwei Zhang, Jinghui Liao, \textbf{Zhenyu Ning}, Jidong Xiao, Kevin Leach, Westley Weimer, and Guojun Wang} % Role
    {[DSN'20] KShot: Live Kernel Patching with SMM and SGX} % Event
    {} % Location
    {} % Date(s)
    {To Appear in the 50th Annual IEEE/IFIP International Conference on Dependable Systems and Networks (DSN'20), Valencia, Spain, 2020.
    }
  \vspace{10pt}
  \cventry
    {\textbf{Zhenyu Ning}, Fengwei Zhang and Weisong Shi} % Role
    {[JCDR'19] A Study of Using TEE on Edge Computing (基于边缘计算的可信执行环境研究)} % Event
    {} % Location
    {} % Date(s)
    {In Journal of Computer Research and Development (计算机研究与发展), Vol.56, No.7, pp.1441-1453, 2019.
    }
    \vspace{10pt}
  \cventry
    {\textbf{Zhenyu Ning}, Fengwei Zhang, and Stephen Remias} % Role
    {[DIMVA'19] Understanding the Security of Traffic Signal Infrastructure} % Event
    {} % Location
    {} % Date(s)
    {In Proceedings of the 16th Conference on Detection of Intrusions and Malware \& Vulnerability Assessment, Gothenburg, Sweden, 2019.
    }
  \vspace{10pt}
  \cventry
    {\textbf{Zhenyu Ning} and Fengwei Zhang} % Role
    {[S\&P'19] Understanding the Security of ARM Debugging Features} % Event
    {} % Location
    {} % Date(s)
    {In Proceedings of the 40th IEEE Symposium on Security \& Privacy, San Francisco, California,
May, 2019.
    }
    \vspace{10pt}
%---------------------------------------------------------
  \cventry
    {\textbf{Zhenyu Ning} and Fengwei Zhang} % Role
    {[TIFS'18] Hardware-assisted Transparent Tracing and Debugging on ARM} % Event
    {} % Location
    {} % Date(s)
    {In IEEE Transactions on Information Forensics \& Security, Vol.14, No.6, pp.1595-1609,
2018.
    }
    \vspace{10pt}
%---------------------------------------------------------
  \cventry
    {\textbf{Zhenyu Ning}, Jinghui Liao, Fengwei Zhang, and Weisong Shi} % Role
    {[EdgeSP'18] Preliminary Study of Trusted Execution Environments on Heterogeneous Edge Platforms} % Event
    {} % Location
    {} % Date(s)
    {In Proceedings of the 1st ACM/IEEE Workshop on Security and Privacy in Edge Computing, in conjunction with the 3rd ACM/IEEE Symposium on Edge Computing (SEC'18), Bellevue, Washington, October, 2018.
    }
    \vspace{10pt}
%---------------------------------------------------------
  \cventry
    {\textbf{Zhenyu Ning} and Fengwei Zhang} % Role
    {[DSN'18] DexLego: Reassembleable Bytecode Extraction for Aiding Static Analysis} % Event
    {} % Location
    {} % Date(s)
    {In Proceedings of the 48th IEEE/IFIP International Conference on Dependable Systems and Networks, Luxembourg, June, 2018.}
    \vspace{10pt}
%---------------------------------------------------------
  \cventry
    {\textbf{Zhenyu Ning} and Fengwei Zhang} % Role
    {[Security'17] Ninja: Towards Transparent Tracing and Debugging on ARM} % Event
    {} % Location
    {} % Date(s)
    {In Proceedings of the 26th USENIX Security Symposium, Vancouver, BC, Canada, August, 2017.}
    \vspace{10pt}
%---------------------------------------------------------
  \cventry
    {\textbf{Zhenyu Ning}, Fengwei Zhang, Weisong Shi, and Larry Shi} % Role
    {[HASP'17] Position Paper: Challenges Towards Securing Hardware-assisted Execution Environments} % Event
    {} % Location
    {} % Date(s)
    {In Proceedings of the Hardware and Architectural Support for Security and Privacy, In conjunction with the 44th International Symposium on Computer Architecture (ISCA), Toronto, ON, Canada, June, 2017.}
    \vspace{10pt}
%---------------------------------------------------------
\end{cventries}
